### 2013-06-24 inst/examples/sensitivity.Rmd
updated sensitivity script

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "myers-cache/", warning=FALSE)
#read_chunk('gaussian-process-control.R')
library(knitcitations)
```

```{r libraries, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
require(tgp)
library(kernlab)
require(MCMCpack)
require(plyr)
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Fixed priors on hyperparameters, fixed model type.

```{r gp-priors}
#inv gamma has mean b / (a - 1) (assuming a>1) and variance b ^ 2 / ((a - 2) * (a - 1) ^ 2) (assuming a>2)
s2.p <- c(5,5)  
tau2.p <- c(5,1)
d.p = c(10, 1/0.1, 10, 1/0.1)
nug.p = c(10, 1/0.1, 10, 1/0.1) # gamma mean
s2_prior <- function(x) dinvgamma(x, s2.p[1], s2.p[2])
tau2_prior <- function(x) dinvgamma(x, tau2.p[1], tau2.p[2])
d_prior <- function(x) dgamma(x, d.p[1], scale = d.p[2]) + dgamma(x, d.p[3], scale = d.p[4])
nug_prior <- function(x) dgamma(x, nug.p[1], scale = nug.p[2]) + dgamma(x, nug.p[3], scale = nug.p[4])
beta0_prior <- function(x, tau) dnorm(x, 0, tau)
beta = c(0)
priors <- list(s2 = s2_prior, tau2 = tau2_prior, beta0 = dnorm, nug = nug_prior, d = d_prior, ldetK = function(x) 0)
```

```{r sdp-pars-fixed}
profit = function(x,h) pmin(x, h)
delta <- 0.01
OptTime = 50  # stationarity with unstable models is tricky thing
reward = 0
xT <- 0

```

```{r RickerAllee-exp}
f <- RickerAllee
p <- c(1.5, 10, 5) 
K <- 10
allee <- 5
```

```{r sdp-pars-explore}
sigma_g <- 0.1
sigma_m <- 0.0
z_g = function() rlnorm(1, 0, sigma_g)
z_m = function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

With parameters `r p`.

```{r }
seed <- round(runif(32) * 1e6)
seed[1] <- 1
seed
yields <- lapply(seed, 
function(seed_i){
  Xo <- K # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=35, nz= 10, 
                 harvest = sort(rep(seq(0, .5, length=7), 5)), seed = seed_i)

  alt <- par_est(obs,  init = c(r=1.5, K=mean(obs$x), s=1))
  est <- par_est_allee(obs, f, p,  init = c(p[1]+1, p[2]-1, p[3]-2, 
                                   s = sigma_g + abs(rnorm(1,0,.1))))

  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)

#  posteriors_plot(gp, priors) # needs trace=TRUE!

  OPT <- optimal_policy(gp, f, est$f, alt$f,
                        p, est$p, alt$p,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g, alt$sigma_g, 
                        delta, xT, profit, reward, OptTime)
  plot_policies(x_grid, OPT$gp_D, OPT$est_D, OPT$true_D, OPT$alt_D)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
})
```

>>>>

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source("~/.knitr_defaults.R")
#opts_knit$set(upload.fun = socialR::flickr.url)
library(knitcitations)
library(nonparametricbayes) 
```

### Model and parameters

```{r stateeq-local}
f <- Myers
p <- c(1.5, 2.5, 8)
K <- 5  # approx, a li'l' less
allee <- 1.2 # approx, a li'l' less
```

Various parameters defining noise dynamics, grid, and policy costs.

```{r sdp-pars, dependson="stateeq-local"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1
x_grid <- seq(0, 1.5 * K, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <-  allee+.5# observations start from
x0 <- K # simulation under policy starts from
Tobs <- 40
MaxT = 1000 # timeout for value iteration convergence
seed <- round(runif(32) * 1e6)
seed[1] <- 1
seed
```

```{r parallel}
require(snowfall)
sfInit(parallel=TRUE, cpu=8)
sfLibrary("nonparametric-bayes")
sfExportAll()
```

32 data-sets from the same model

```{r }
yields <- sfSapply(seed, 
function(seed_i){

  x <- numeric(Tobs)
  x[1] <- Xo
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)
  obs <- data.frame(x = c(rep(0,nz), 
                          pmax(rep(0,Tobs-1), x[1:(Tobs-1)])), 
                    y = c(rep(0,nz), 
                          x[2:Tobs]))

  ## @knitr gp-priors
  s2.p <- c(5,5)  
  d.p = c(10, 1/0.1)

  ## @knitr gp
  gp <- gp_mcmc(obs$x, y=obs$y, n=1e5, s2.p = s2.p, d.p = d.p)
  gp_dat <- gp_predict(gp, x_grid, burnin=1e4, thin=300)

  matrices_gp <- gp_transition_matrix(gp_dat$Ef_posterior, gp_dat$Vf_posterior, x_grid, h_grid) 
  opt_gp <- value_iteration(matrices_gp, x_grid, h_grid, MaxT, xT, profit, delta, reward)

  ## @knitr mle-opt
  matrices_true <- f_transition_matrix(f, p, x_grid, h_grid, sigma_g)
  opt_true <- value_iteration(matrices_true, x_grid, h_grid, OptTime=MaxT, xT, profit, delta=delta)

  OPT = data.frame(GP = opt_gp$D, True = opt_true$D)
  policies <- melt(data.frame(stock=x_grid, sapply(OPT, function(x) x_grid[x])), id="stock")
  names(policies) <- c("stock", "method", "value")

  sims <- lapply(OPT, function(D){
    set.seed(1)
    lapply(1:100, function(i) 
      ForwardSimulate(f, p, x_grid, h_grid, x0, D, z_g, profit=profit, OptTime=OptTime)
    )
  })

  dat <- melt(sims, id=names(sims[[1]][[1]]))
  sims_data <- data.table(dat)
  setnames(sims_data, c("L1", "L2"), c("method", "reps")) 
  # Legend in original ordering please, not alphabetical: 
  sims_data$method = factor(sims_data$method, ordered=TRUE, levels=names(OPT))

  Profit <- sims_data[, sum(profit), by=c("reps", "method")]
  tmp <- dcast(Profit, reps ~ method)
  tmp <- tmp / tmp[,"True"]
  tmp <- melt(tmp[2:dim(tmp)[2]])
  actual_over_optimal$GP

})
```
